Easy as Pi: A Network Coding Raspberry Pi Testbed

### 2016-06-03 testbed.tex
changed scripts
added current measurements

This section will be used to present a Raspberry Pi testbed and the steps to
install and configure the individual devices.

The testbed is depicted in figure~\ref{fig:testbed_setup}. It consists of twenty
Raspberry Pi 1 model B rev 2 (Rasp\_01 to Rasp\_20) and 
ten Raspberry Pi 2 model b V1.1 (Rasp2\_01 to Rasp2\_10).

The goal is to configure all the devices identically with the same software
and configurations. There are however a few differences between them that we
need to take into account. E.g. hostname and network addresses.

@@

\begin{figure}[ht!]
\centering
\includegraphics[width=0.6\textwidth]{images/testbed_setup.eps}
\caption{Testbed setup}
\label{fig:testbed_setup}
\end{figure}

@@

@@

@@

% MAC and Hostname file
\Suppressnumber\begin{lstlisting}[]
<@\textcolor{gray}{\$\{ROOTDIR\}/home/pi/rasp\_config/nodes.csv}@>
<@\textcolor{gray}{
---------------------------------------------------------------}
\Reactivatenumber @>
# Ethernet MAC    Hostname
b8:27:eb:5b:da:20 rasp_00
b8:27:eb:7b:c3:91 rasp_01
b8:27:eb:54:9c:64 rasp_02
b8:27:eb:95:bd:11 rasp_03
\end{lstlisting}
\FloatBarrier

@@

% Create an initramfs
\begin{lstlisting}[]
# mkinitramfs -o /boot/init.gz
# mkinitramfs -o /boot/init.gz -k 4.4.11+
\end{lstlisting}
\FloatBarrier

@@

% Exit chroot, umount, and write to memory card
\begin{lstlisting}[]
# exit
# cd ..
# umount --recursive ${ROOTDIR}
# losetup -d WHICH_NUMBE.img of=/dev/mmcblk0 bs=4MR
# dd if=${IMAGE}.img of=/dev/mmcblk0 bs=4M
\end{lstlisting}
\FloatBarrier

>>>>

\begin{figure}[ht!]
\centering
\includegraphics[width=0.6\textwidth]{images/testbed_setup2.eps}
\caption{Testbed setup}
\label{fig:testbed_setup}
\end{figure}

This section will present a testbed of thirty \ac{Raspi}s.
%Twenty \ac{Raspi} 1 model B revision 2 and ten \ac{Raspi} 2 model B V1.1.
They are all equipped with a memory card and are connected to the
university network by wire using their ethernet interface (eth0).

To easily discover the \ac{Raspi}s within the university network, they have all
been assigned a unique name under a common domain.
This eliminates the need to remember their individual \ac{IP}s.

A sketch of the testbed is depicted in figure~\ref{fig:testbed_setup}.
We have two types of \ac{Raspi}s in our setup.
Table \ref{tab:rasp_naming} shows the naming convention.

\begin{table}[ht!]
  \centering
  \begin{tabular}{|c|c|}
    \hline
      \textbf{Hostname} & \textbf{Model} \\ \hline
    Rasp00 - Rasp19 & Raspberry Pi 1 model B rev. 2 \\ \hline
    Rasp100 - Rasp109 & Rasperry Pi 2 model B V1.1 \\ \hline
  \end{tabular}
  \caption{Raspberry Pi naming convention}
  \label{tab:rasp_naming}
\end{table}

Accessing them is easily done using \ac{SSH}.
To address them within the university network, 
The \ac{Raspi}s

The Raspberry Pis are all equipped with an ethernet interface (eth0) and
connected by wire to the university's \ac{LAN}. The university network
administration was provided
the \ac{MAC} addresses of the ethernet interfaces to automatically assign
the devices the desired \ac{IP} addresses as shown in the figure. In a personal
\ac{LAN}, another option could be to manually provide the devices with static
\ac{IP}s.

This section will be used to present a \ac{Raspi} testbed and the steps to
install and configure its devices.

The testbed is depicted in figure~\ref{fig:testbed_setup}. It consists of twenty
Raspberry Pi 1 model B rev 2 (Rasp01 to Rasp20) and 
ten Raspberry Pi 2 model b V1.1 (Rasp2\_01 to Rasp2\_10).

The goal is to configure all the \ac{Raspi}s identically with the same software
and configurations. There are however a few differences between them that we
need to take into account. E.g. hostname and network addresses.

@@

@@

\subsection{Download image}

@@

\subsection{Mount image}

@@

% MAC and Hostname file
\Suppressnumber\begin{lstlisting}[]
<@\textcolor{gray}{\$\{ROOTDIR\}/home/pi/rasp\_config/nodes.csv}@>
<@\textcolor{gray}{
---------------------------------------------------------------}
\Reactivatenumber @>
# Ethernet MAC    Hostname
b8:27:eb:5b:da:20 rasp00
b8:27:eb:7b:c3:91 rasp01
b8:27:eb:54:9c:64 rasp02
b8:27:eb:95:bd:11 rasp03
\end{lstlisting}
\FloatBarrier

@@

% Create an initramfs
\begin{lstlisting}[]
# How to i know the kernel version /lib/modules/
# mkinitramfs -o /boot/init.gz -k 4.4.11+
\end{lstlisting}
\FloatBarrier

@@

% Exit chroot, umount, and write to memory card
\begin{lstlisting}[]
# exit
# cd ..
# umount --recursive ${ROOTDIR}
# losetup -d WHICH_NUMBE.img
# dd if=${IMAGE}.img of=/dev/mmcblk0 bs=4M
\end{lstlisting}
\FloatBarrier

How about kodo python?
